$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-11-05 qdpm_paper.tex
Moved correlation function to appendix
Added Bragg peak scaling figure
z3
Worked on text

Here we discuss the dimer density correlations in the RK ground state of the QDPM. In \figref{fig:dimer_vison_heatmap} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice. The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
\begin{equation}
S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
\end{equation}
where we restrict the sum to horizontal links, for an $L=32$ lattice. \figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone. The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$. The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice. The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off the given scale. ({\it right}) The $Z_3$ magnetic string correlation function $C_M(\bm{r}_{\bm{0}p})$, where the the correlations is with respect to the blue plaquette. \note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
        \label{fig:dimer_vison_heatmap}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated. ({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
        \label{fig:structure_factor} 
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the $Z_3$ magnetic string structure factor $S_M$ ({\it bottom})
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. Switch the y-axis from $S_v\rightarrow S_M$.}}
        \label{fig:structure_factor_path}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking. For rotational symmetry breaking we define 
\begin{equation}
\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
\end{equation}
where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking. to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$ 
\begin{align}
\Mperp \equiv  \frac{8}{L^2} \sum_{\Box} \Bigl(  &(-1)^{r_x} \theta\left(\Mrot \right) \Pi_\Box^v \notag\\
+ &(-1)^{r_y}\theta\left(-\Mrot \right) \Pi_\Box^h\Bigr) \label{eq:Mperp},
\end{align}
where $\theta(x)$ is the Heaviside function, and $\Pi_\Box^h$ ($\Pi_\Box^v$) is one if the plaquette $\Box$ has two horizontal (vertical) dimers, and zero otherwise. Similarly, we define $\Mpar$ to be given by \Eqref{eq:Mperp} with $r_x$ and $r_y$ swapped between terms. Additionally, we define order parameters that indicate ``columnar" and ``staggered" dimer order~\cite{Syljuasen2005}:
\begin{align}
\MstagSq \equiv  \frac{1}{4L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
\end{align}
\begin{align}
\McolSq \equiv  \frac{1}{4L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+ &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},
\end{align}
where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links. In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[]
    \centering
    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
    \label{fig:order_params}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Additionally we have studied the nature of the decay of the connected dimer-dimer correlation function,
  \begin{equation}
    C_{\mathrm{d}} \left(r\right) \equiv \langle n_{\bm{0}} n_{\bm{r}} \rangle - \langle n_{\bm{0}} \rangle   \langle n_{\bm{r}} \rangle   
\end{equation}
where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$. In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, \textcolor{red}{for both $r$ parallel and perpendicular to the orientation of the dimers} \note{(Owen: can you add both directions to this plot?)} for an $L=64$ lattice. We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$; additionally we find that correlations between perpendicular dimers also decay exponentially.

Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the

@@

To investigate the $Z_3$ gauge theory description of the QDPM RK ground state, we study the $Z_3$ magnetic string correlation function as defined in \eqref{eq:Sgamma} \& \eqref{eq:SQDPM}:
\begin{equation}
C_M \left( \bm{r}_{pp'} \right) \equiv \left \langle \exp \left[ \frac{2 \pi}{3} i \left( \Phi_{\gamma_{pp'}} -\tilde{\Phi}_{\gamma_{pp'}} \right) \right] \right \rangle
\end{equation}
where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$. \note{Something about the background dimerization and gauge fixing here. Are we using the real parts or $\sqrt{C_M^*C_M}$?}

In \figref{fig:dimer_vison_heatmap}, we have ploted $C_M$ for an $L=16$ lattice, which displays short distance correlations that quickly decay. \note{Comment here about gauge fixing breaking symmetry, if still present...}. Additionally, we have plotted the magnetic string structure factor
\begin{equation}
S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot r_{pp'}} C_M\left( \bm{r}_{pp'}\right)
\end{equation}
in \figref{fig:structure_factor}. \note{Discuss any effect of gauge fixing here, if relevant}.

\figref{fig:vison_cor} show the decay of $C_M$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}

Thus we find no evidence of magnetic vortex condensation on lattices up to $L=64$.

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
    \caption{ $Z_3$ magnetic string correlation $C_M$ along along one axis of an $L=64$ lattice. The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
    \label{fig:vison_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers. We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
\begin{equation}
\monomermvA  \Longleftrightarrow \monomermvB
\end{equation}
which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space. Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices.

We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlation}. If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations. In \figref{fig:monomer_correlations}, the horizontal lines correspond to $L^{-4}$ for each system size; we find that the monomer correlations quickly decay to $L^{-4}$ indicating a deconfinement of monomers.

%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Monomer correlations}

%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}. The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color. \note{Owen: Do you have data for $L=64$? Can you make the subscripts in the y-axis label bold math? Maybe we should renomalize this plot by a factor of $L^2$. This is only one sub-lattice--what about the other sublattice?}}
        \label{fig:monomer_correlations}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
    \begin{tabular}{| l | c | c |}
  	\hline
     & $c$ & $\bar{c}$ \\
	\hline
    $i$ & $\monomermvA$ &  $\monomermvB$  \\
    \hline
  \end{tabular}
  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
  \label{tab:pentamerMoves}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

@@

We can define two oriented open string operators which commute with $H_{Z_3}$ everywhere except at the endpoints. The electric string operator $S_e$, which acts on an open, oriented string on the lattice $\gamma_{vv'}$ with endpoints $v,v'$, and creates a $+1$ ($-1$) charge at vertex $v$ ($v')$, is defined as
\begin{equation}
    S_e \left( \gamma_{vv'} \right) \equiv \prod_{l \in \gamma_{vv'}} Q_{v_l v_l'}^\dagger
\end{equation}
where the product is over all links $l$ in $\gamma_{vv'}$, $v_l$ and $v_l'$ are the two vertices in $l$, ordered according to the orientation of $\gamma_{vv'}$ (see \figref{fig:example_elec_string}). The magnetic string operator $S_m$ is defined by an open, oriented string on the dual lattice and creates a magnetic vortex-antivortex pair on plaquettes at the endpoints of $\tilde{\gamma}_{pp'}$
\begin{equation}
    S_m \left( \tilde{\gamma}_{vv'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
\end{equation}
where the product is over all links $l$ that cross $\tilde{\gamma}$ and $v_l$ ($v_l'$) is the vertex to the left (right) of the string as $\tilde{\gamma}$ is traversed from $p$ to $p'$. 
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
    \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration. The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the red to blue vertex. ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel. \note{Owen: Can you remove the a) and b) labels on the figure? Also switch the $\Gamma$ to $\gamma$, and remove the $v_0-v_3$ labels. Add a gray arrow on the string operator from red to blue. Can you add a non-trivial magnetic loop around the blue charge on the right?} }
    \label{fig:example_elec_string}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\section{Additional numerical results on the QDPM RK ground state}
%
%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%    \centering
%    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
%    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
%    sub-lattice for a $L=64$ lattice.}
%    \label{fig:spatial_dmr_cor}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Here we discuss the dimer density correlations in the RK ground state of the QDPM. In \figref{fig:dimer_vison_heatmap} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice. The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
\begin{equation}
S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
\end{equation}
where we restrict the sum to horizontal links, for an $L=32$ lattice. \figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone. The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$. The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.
We have plotted the finite size scaling of the intensity of these peaks in  \figref{fig:bragg_scaling}, which we find to vanish in the thermodynamic limit. These maxima at $(0,\pi)$ and $(\pi,\pi)$ are thus consistent with finite size effects due to short distance correlations. Thus we see no evidence of thermodynamic limit symmetry breaking.

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice. The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off the given scale. ({\it right}) The magnitude of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$, where the the correlations is with respect to the blue plaquette. \note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
        \label{fig:dimer_vison_heatmap}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated. ({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
        \label{fig:structure_factor} 
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ ({\it bottom})
        shown along a path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. Switch the y-axis from $S_v\rightarrow S_M$.}}
        \label{fig:structure_factor_path}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{peak_scaling.pdf}
    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($|S_M|$) structure factors. All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid. \note{Owen: We don't need the absolute value bars for $S_d$ since it's real.}}
    \label{fig:bragg_scaling}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Additionally we have studied the nature of the decay of the connected dimer-dimer correlation function,
  \begin{equation}
    C_{\mathrm{d}} \left(r\right) \equiv \langle n_{\bm{0}} n_{\bm{r}} \rangle - \langle n_{\bm{0}} \rangle   \langle n_{\bm{r}} \rangle   
\end{equation}
where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$. In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, \textcolor{red}{for both $r$ parallel and perpendicular to the orientation of the dimers} \note{(Owen: can you add both directions to this plot?)} for an $L=64$ lattice. We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$. Additionally, $C_d$ displays a sub-lattice oscillation that is consistent with the finite-size maximum in $S_d$ at $(0,\pi)$. Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the QDM.

@@

To investigate the $Z_3$ gauge theory description of the QDPM RK ground state, we study the $Z_3$ magnetic string correlation function as defined in \eqref{eq:Sgamma} \& \eqref{eq:SQDPM}:
\begin{equation}
C_M \left( \bm{r}_{pp'} \right) \equiv \left \langle \exp \left[ \frac{2 \pi}{3} i \left( \Phi_{\gamma_{pp'}} -\tilde{\Phi}_{\gamma_{pp'}} \right) \right] \right \rangle
\end{equation}
where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$. In \figref{fig:dimer_vison_heatmap}, we have plotted $|C_M|$ for an $L=16$ lattice. Note, that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization. Additionally, we have computed the magnetic string structure factor
\begin{equation}
S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot r_{pp'}} C_M\left( \bm{r}_{pp'}\right)
\end{equation}
and plot the magnitude $|S_M$ in \figref{fig:structure_factor}. We have chosen d a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{fig:BKGD_dimers}\note{Where should we show the background dimerization??}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction. \note{Owen: What are the effects of the background dimerization?}. While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$) \note{(Owen: What about $(\pi,\pi)$??)}. We have plotted the finite-size scaling of these peaks in \figref{fig:bragg_scaling} which demonstrates that these peaks vanish in the thermodynamic limit. While the vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, the vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}. \figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}. These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of an $L=64$ lattice. The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
    \label{fig:vison_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

To study the confinement of $Z_3$ electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers. We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
\begin{equation}
\monomermvA  \Longleftrightarrow \monomermvB
\end{equation}
which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space. Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices. We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlations}. If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations. \figref{fig:monomer_correlations} demonstrates that $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ decays to $L^{-4}$ for each system size, indicating a deconfinement of monomers.
%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}
%    \begin{tabular}{| l | c | c |}
%  	\hline
%     & $c$ & $\bar{c}$ \\
%	\hline
%    $i$ & $\monomermvA$ &  $\monomermvB$  \\
%    \hline
%  \end{tabular}
%  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
%  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
%  \label{tab:pentamerMoves}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to $L=64$. The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color. \note{Owen: Make the subscripts in the y-axis label bold math. Extend the horizontal lines all the way across the plot. Remove the legend bounding box and use one symbol for each legend entry. Remove the black boundaries of the symbols.}}
        \label{fig:monomer_correlations}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

We can define two oriented open string operators which commute with $H_{Z_3}$ everywhere except at the endpoints. The electric string operator $S_e$, which acts on an open, oriented string on the lattice $\gamma_{vv'}$ with endpoints $v,v'$, and creates a $+1$ ($-1$) charge at vertex $v$ ($v')$, is defined as
\begin{equation}
    S_e \left( \gamma_{vv'} \right) \equiv \prod_{l \in \gamma_{vv'}} Q_{v_l v_l'}^\dagger
\end{equation}
where the product is over all links $l$ in $\gamma_{vv'}$, $v_l$ and $v_l'$ are the two vertices in $l$, ordered according to the orientation of $\gamma_{vv'}$ (see \figref{fig:example_elec_string}). The magnetic string operator $S_m$ is defined by an open, oriented string on the dual lattice and creates a magnetic vortex-antivortex pair on plaquettes at the endpoints of $\tilde{\gamma}_{pp'}$
\begin{equation}
    S_m \left( \tilde{\gamma}_{vv'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
\end{equation}
where the product is over all links $l$ that cross $\tilde{\gamma}$ and $v_l$ ($v_l'$) is the vertex to the left (right) of the string as $\tilde{\gamma}$ is traversed from $p$ to $p'$. 
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
    \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration. The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the red to blue vertex. ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel. \note{Owen: Can you remove the a) and b) labels on the figure? Also switch the $\Gamma$ to $\gamma$, and remove the $v_0-v_3$ labels. Add a gray arrow on the string operator from red to blue. Can you add a non-trivial magnetic loop around the blue charge on the right?} }
    \label{fig:example_elec_string}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%    \centering
%    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
%    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
%    sub-lattice for a $L=64$ lattice.}
%    \label{fig:spatial_dmr_cor}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Additional numerical results on the QDPM RK ground state}
%
%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%    \centering
%    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
%    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
%    sub-lattice for a $L=64$ lattice.}
%    \label{fig:spatial_dmr_cor}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking. For rotational symmetry breaking we define 
\begin{equation}
\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
\end{equation}
where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking. to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$ 
\begin{align}
\Mperp \equiv  \frac{8}{L^2} \sum_{\Box} \Bigl(  &(-1)^{r_x} \theta\left(\Mrot \right) \Pi_\Box^v \notag\\
+ &(-1)^{r_y}\theta\left(-\Mrot \right) \Pi_\Box^h\Bigr) \label{eq:Mperp},
\end{align}
where $\theta(x)$ is the Heaviside function, and $\Pi_\Box^h$ ($\Pi_\Box^v$) is one if the plaquette $\Box$ has two horizontal (vertical) dimers, and zero otherwise. Similarly, we define $\Mpar$ to be given by \Eqref{eq:Mperp} with $r_x$ and $r_y$ swapped between terms. Additionally, we define order parameters that indicate ``columnar" and ``staggered" dimer order~\cite{Syljuasen2005}:
\begin{align}
\MstagSq \equiv  \frac{1}{L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
\end{align}
\begin{align}
\McolSq \equiv  \frac{1}{L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+ &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},
\end{align}
where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links. In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[]
    \centering
    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
    \label{fig:order_params}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
